---
title: "MeaningPE_Analysis"
author: "JR"
date: "7 5 2020"
output: html_document
---
## Intro
I have been reusing the same code for many different variable combinations, priors, link function and saved with file function. Therefore, the prior in the code doesn't have to reflect the output of the model you will get when you run the code.

## Packages, data
```{r}
## package
pacman::p_load(ggplot2, brms, readxl, tidyverse, plyr, reader, brms, MASS, ggpubr, fitdistrplus, actuar, rethinking, viridis, bayesplot, vcd, rcompanion)

color_scheme_set("viridis")



## data
demo_ques <- read_csv(file = "Data/Demo_ques_clean.csv")

demo_ques[,c(3:13,15:18)] <- lapply(demo_ques[,c(3:13,15:18)], as.factor)

MLQ <- read_csv(file = "Data/MLQ_long_clean.csv", col_types = cols(
  ID = col_character(),
  MLQ_QN = col_factor(),
  MLQ_b_p_ques = col_factor(),
  MLQ_b_p_score = col_integer(),
  MLQ_b_s_ques = col_factor(),
  MLQ_b_s_score = col_integer(),
  MLQ_2wa_s_ques = col_factor(),
  MLQ_2wa_s_score = col_integer(),
  MLQ_2wa_p_ques = col_factor(),
  MLQ_2wa_p_score = col_integer(),
  MLQ_4wa_p_ques = col_factor(),
  MLQ_4wa_p_score = col_integer(),
  MLQ_4wa_s_ques = col_factor(),
  MLQ_4wa_s_score = col_integer()
))
# making super df
MLQ <- merge(MLQ, demo_ques, by = "ID")
summary(MLQ)

# scaling
MLQ$Confidence_in_long_lasting_effect_PE <- scale(MLQ$Confidence_in_long_lasting_effect_PE)

MLQ <- mutate(MLQ,
              ASC_average = apply(MLQ[,37:47], 1, na.rm = TRUE, sum)/11)

MLQ <- mutate(MLQ,
              EBI_scale = scale(EBI_sum),
              ASC_scale = scale(ASC_average),
              EDI_scale = scale(EDI_total),
              CEQ_scale = scale(CEQ_Total),
              MEQ_scale = scale(MEQ_Total))

MLQ$Intended_drug_use <- paste(MLQ$Intended_drug_use, MLQ$Intended_drug_use_other)

## demo info
demo_data <- demo_ques[,c(1:7, 11, 15)]
demo_data <- na.omit(demo_data)

psych::describe(demo_data)
summary(demo_data)
```

## Identifying distribution
```{r}
# identifying outcome distribution

my_data <- MLQ$MLQ_b_p_score
my_data <- as.numeric(as.character(na.omit(my_data)))

fit_ln <- fitdist(my_data, "lnorm", discrete = TRUE)
fit_norm <- fitdist(my_data, "norm", discrete = TRUE)
fit_ll <- fitdist(my_data, "llogis", discrete = TRUE)
fit_uni <- fitdist(my_data, "unif", discrete = TRUE)
fit_logis <- fitdist(my_data, "logis", discrete = TRUE)

cdfcomp(list(fit_ln, fit_norm, fit_ll, fit_logis),
        legendtext = c("lognormal", "normal", "log-logistic", "logis"), lwd=2)

gofstat(list(fit_ln, fit_norm, fit_ll, fit_logis), fitnames = c("lognormal", "normal", "log-logistic", "logis"))


```






## MLQ Pb2wa
MLQ changes in first dimension (presence) before vs 2 weeks after
```{r}
### MLQ PRESENT BEFORE VS 2 WEEKS AFTER

#data transformation
MLQ_p_b2wa <- pivot_longer(
  MLQ, c(MLQ_b_p_score, MLQ_2wa_p_score), names_to = "MLQ_p_b2wa_type", values_to = "MLQ_p_b2wa_score")

MLQ_p_b2wa <- MLQ_p_b2wa[,c(1:2, 13:47)]


summary(MLQ_p_b2wa)
# formula
MLQ_p_b2wa_f <- bf (MLQ_p_b2wa_score ~ 1 +  MLQ_p_b2wa_type + (1|ID) + (1|MLQ_QN))


get_prior(MLQ_p_b2wa_f, MLQ_p_b2wa, family = cumulative())


MLQ_p_b2wa_prior <- c(
  prior(student_t(3, 0, 10), class = Intercept),
  prior(normal(0, 1), class = b, coef = "MLQ_p_b2wa_typeMLQ_b_p_score"),
  prior(normal(0, 1),   class = sd)
)

MLQ_p_b2wa_mp<- brm(
  formula = MLQ_p_b2wa_f,
  data = MLQ_p_b2wa,
  family = cumulative("probit"),
  prior = MLQ_p_b2wa_prior,
  sample_prior = "only",
  chains = 3,
  cores = 3,
  control = list(max_treedepth = 20, adapt_delta = 0.99))

# better prior check, b2wa
summary(MLQ_p_b2wa_mp)
pp_check(MLQ_p_b2wa_mp, type = "bars", nsamples = 100) +
  ggtitle("Before vs 2 weeks after prior predictive check")
  
## posterior model b2wa
MLQ_p_b2wa_m<- brm(
  formula = MLQ_p_b2wa_f,
  data = MLQ_p_b2wa,
  family = cumulative("probit"),
  prior = MLQ_p_b2wa_prior,
  sample_prior = T,
  chains = 3,
  cores = 3,
  inits = 0,
  iter = 2000,
  control = list(max_treedepth = 15, adapt_delta = 0.999),
  file = "model_files/MLQ_p_b2wa_m_probit_otherPE")

## pp checks b2wa
pp_check(MLQ_p_b2wa_m, nsamples = 100, type = "bars")+
  ggtitle("Before vs 2 weeks after Posterior predictive check")

summary(MLQ_p_b2wa_m)

plot(MLQ_p_b2wa_m)

## chain check b2wa
mcmc_trace(MLQ_p_b2wa_m, pars = c("b_Intercept[1]","b_Intercept[2]","b_Intercept[3]","b_Intercept[4]","b_Intercept[5]","b_Intercept[6]", "b_MLQ_p_b2wa_typeMLQ_b_p_score", "sd_ID__Intercept", "sd_MLQ_QN__Intercept" )) + theme_classic()

mcmc_rank_overlay(MLQ_p_b2wa_m, pars = c("b_Intercept[1]","b_Intercept[2]","b_Intercept[3]","b_Intercept[4]","b_Intercept[5]","b_Intercept[6]", "b_MLQ_p_b2wa_typeMLQ_b_p_score", "sd_ID__Intercept", "sd_MLQ_QN__Intercept" )) + theme_classic()


## hypothesis testing  b2wa
hypothesis(MLQ_p_b2wa_m, "Other_PE_2waYes < 0")
hypothesis(MLQ_p_b2wa_m, "MLQ_p_b2wa_typeMLQ_b_p_score < 0")

hypothesis(MLQ_p_b2wa_m, "MLQ_p_b2wa_typeMLQ_b_p_score < 0")

summary((readRDS("model_files/MLQ_p_b2wa_m_probit_otherPE.rds")))
conditional_effects(MLQ_p_b2wa_m, categorical = TRUE)
```

## MLQ Pb4wa
MLQ changes in first dimension (presence) before vs 4 weeks after
```{r}
### MLQ PRESENT BEFORE VS 4 WEEKS AFTER

#data transformation
MLQ_p_b4wa <- pivot_longer(
  MLQ, c(MLQ_b_p_score, MLQ_4wa_p_score), names_to = "MLQ_p_b4wa_type", values_to = "MLQ_p_b4wa_score")

MLQ_p_b4wa <- MLQ_p_b4wa[,c(1:2, 13:47)]

summary(MLQ_p_b4wa)
#MLQ_p_b4wa <- na.omit(MLQ_p_b4wa )

# formula
MLQ_p_b4wa_f <- bf (MLQ_p_b4wa_score ~ 1 +  MLQ_p_b4wa_type + Other_PE_4wa +(1|ID)+ (1|MLQ_QN))


get_prior(MLQ_p_b4wa_f, MLQ_p_b4wa, family = cumulative())


MLQ_p_b4wa_prior <- c(
  prior(student_t(3, 0, 10), class = Intercept),
  prior(normal(0, 1), class = b, coef = "MLQ_p_b4wa_typeMLQ_b_p_score"),
  prior(normal(0, 1), class = b, coef = "Other_PE_4waYes"),
  prior(normal(0, 1),   class = sd)
)


MLQ_p_b4wa_mp<- brm(
  formula = MLQ_p_b4wa_f,
  data = MLQ_p_b4wa,
  family = cumulative("probit"),
  prior = MLQ_p_b4wa_prior,
  sample_prior = "only",
  chains = 3,
  cores = 3,
  control = list(max_treedepth = 15, adapt_delta = 0.99),
  file = "model_files/MLQ_p_b4wa_mp")

# better prior check, b4wa
summary(MLQ_p_b4wa_mp)
pp_check(MLQ_p_b4wa_mp, type = "bars", nsamples = 100) +
  ggtitle("Before vs 4 weeks after prior predictive check")
  
## posterior model b4wa
MLQ_p_b4wa_m<- brm(
  formula = MLQ_p_b4wa_f,
  data = MLQ_p_b4wa,
  family = cumulative("probit"),
  prior = MLQ_p_b4wa_prior,
  sample_prior = T,
  chains = 3,
  cores = 3,
  iter = 2000,
  control = list(max_treedepth = 15, adapt_delta = 0.999),
  file = "model_files/MLQ_p_b4wa_final")

## pp checks b4wa
pp_check(MLQ_p_b4wa_m, nsamples = 100, type = "bars")+
  ggtitle("Before vs 4 weeks after Posterior predictive check")

summary(MLQ_p_b4wa_m)

plot(MLQ_p_b4wa_m)

## chain check b4wa
mcmc_trace(MLQ_p_b4wa_m, pars = c("b_Intercept[1]")) + theme_classic()
mcmc_rank_overlay(MLQ_p_b4wa_m, pars = c()) + theme_classic()


## hypothesis testing  b4wa
hypothesis(MLQ_p_b4wa_m, "MLQ_p_b4wa_typeMLQ_b_p_score < 0")

hypothesis(MLQ_p_b4wa_m, "Other_PE_4waYes > 0")
plot(hypothesis(MLQ_p_b4wa_m, "MLQ_p_b4wa_typeMLQ_b_p_score < 0"))

summary(readRDS(file = "model_files/MLQ_p_b4wa_m_prob_consprior.rds"))




conditional_effects(MLQ_p_b4wa_m, categorical = TRUE)
```


##MLQ Sb2wa
MLQ changes in the second dimension (search) before vs 2 weeks after
```{r}
### MLQ SEARCH BEFORE VS 2 WEEKS AFTER

#data transformation
MLQ_s_b2wa <- pivot_longer(
  MLQ, c(MLQ_b_s_score, MLQ_2wa_s_score), names_to = "MLQ_s_b2wa_type", values_to = "MLQ_s_b2wa_score")

MLQ_s_b2wa <- MLQ_s_b2wa[,c(1:2, 13:47)]



# formula
MLQ_s_b2wa_f <- bf (MLQ_s_b2wa_score ~ 1 +  MLQ_s_b2wa_type + Other_PE_2wa +(1|ID) + (1|MLQ_QN))


get_prior(MLQ_s_b2wa_f, MLQ_s_b2wa, family = cumulative())


MLQ_s_b2wa_prior <- c(
  prior(student_t(3, 0, 10), class = Intercept),
  prior(normal(0, 1), class = b, coef = "MLQ_s_b2wa_typeMLQ_b_s_score"),
  prior(normal(0, 1), class = b, coef = "Other_PE_2waYes"),
  prior(normal(0, 1),   class = sd)
)

MLQ_s_b2wa_mp<- brm(
  formula = MLQ_s_b2wa_f,
  data = MLQ_s_b2wa,
  family = cumulative("probit"),
  prior = MLQ_s_b2wa_prior,
  sample_prior = "only",
  chains = 3,
  cores = 3,
  control = list(max_treedepth = 15, adapt_delta = 0.99))

# better prior check, SEARCH b2wa
summary(MLQ_s_b2wa_mp)
pp_check(MLQ_s_b2wa_mp, type = "bars", nsamples = 100) +
  ggtitle("Before vs 2 weeks after prior predictive check of Search")
  
## posterior model: SEARCH b2wa
MLQ_s_b2wa_m<- brm(
  formula = MLQ_s_b2wa_f,
  data = MLQ_s_b2wa,
  family = cumulative("probit"),
  prior = MLQ_s_b2wa_prior,
  sample_prior = T,
  chains = 3,
  cores = 3,
  iter = 2000,
  control = list(max_treedepth = 15, adapt_delta = 0.999),
  file = "model_files/MLQ_s_b2wa_m_final")

## pp checks b2wa
pp_check(MLQ_s_b2wa_m, nsamples = 100, type = "bars")+
  ggtitle("Before vs 2 weeks after Posterior predictive check Search, Search")

summary(MLQ_s_b2wa_m)

plot(MLQ_s_b2wa_m)
## chain check b2wa
mcmc_trace(MLQ_s_b2wa_m, pars = c("b_Intercept[1]")) + theme_classic()
mcmc_rank_overlay(MLQ_s_b2wa_m) + theme_classic()


## hypothesis testing  b2wa
hypothesis(MLQ_s_b2wa_m, "MLQ_s_b2wa_typeMLQ_b_s_score > 0")
plot(hypothesis(MLQ_s_b2wa_m, "MLQ_s_b2wa_typeMLQ_b_s_score < 0"))

conditional_effects(MLQ_s_b2wa_m, categorical = TRUE)
hypothesis(MLQ_s_b2wa_m, "Other_PE_2waYes > 0")
```

## MLQ Sb4wa
MLQ changes in the second dimension (search) before vs 4 weeks after
```{r}
### MLQ SEARCH BEFORE VS 4 WEEKS AFTER

#data transformation
MLQ_s_b4wa <- pivot_longer(
  MLQ, c(MLQ_b_s_score, MLQ_4wa_s_score), names_to = "MLQ_s_b4wa_type", values_to = "MLQ_s_b4wa_score")

MLQ_s_b4wa <- MLQ_s_b4wa[,c(1:2, 13:47)]

MLQ_s_b4wa <- na.omit(MLQ_s_b4wa )

# formula
MLQ_s_b4wa_f <- bf (MLQ_s_b4wa_score ~ 1 +  MLQ_s_b4wa_type + Other_PE_4wa + (1|ID) + (1|MLQ_QN))


get_prior(MLQ_s_b4wa_f, MLQ_s_b4wa, family = cumulative())


MLQ_s_b4wa_prior <- c(
  prior(student_t(3, 0, 10), class = Intercept),
  prior(normal(0, 1), class = b, coef = "MLQ_s_b4wa_typeMLQ_b_s_score"),
  prior(normal(0, 1), class = b, coef = "Other_PE_4waYes"),
  prior(normal(0, 1),   class = sd)
)

MLQ_s_b4wa_mp<- brm(
  formula = MLQ_s_b4wa_f,
  data = MLQ_s_b4wa,
  family = cumulative("probit"),
  prior = MLQ_s_b4wa_prior,
  sample_prior = "only",
  chains = 3,
  cores = 3,
  control = list(max_treedepth = 15, adapt_delta = 0.99),
  file = "model_files/MLQ_s_b4wa_mp2")

# better prior check, SEARCH b4wa
summary(MLQ_s_b4wa_mp)
pp_check(MLQ_s_b4wa_mp, type = "bars", nsamples = 100) +
  ggtitle("Before vs 4 weeks after prior predictive check of Search")
  
## posterior model: SEARCH b4wa
MLQ_s_b4wa_m<- brm(
  formula = MLQ_s_b4wa_f,
  data = MLQ_s_b4wa,
  family = cumulative("probit"),
  prior = MLQ_s_b4wa_prior,
  sample_prior = T,
  chains = 3,
  cores = 3,
  iter = 2000,
  control = list(max_treedepth = 15, adapt_delta = 0.999),
  file = "model_files/MLQ_s_b4wa_m_probit")

## pp checks  search b4wa
pp_check(MLQ_s_b4wa_m, nsamples = 100, type = "bars")+
  ggtitle("Before vs 4 weeks after Posterior predictive check Search")

summary(MLQ_s_b4wa_m)

plot(MLQ_s_b4wa_m)
## chain check search b4wa
mcmc_trace(MLQ_s_b4wa_m, pars = c("b_Intercept[1]","b_Intercept[2]","b_Intercept[3]","b_Intercept[4]","b_Intercept[5]","b_Intercept[6]", "b_MLQ_s_b4wa_typeMLQ_b_s_score", "sd_ID__Intercept", "sd_MLQ_QN__Intercept" )) + theme_classic()
mcmc_rank_overlay(MLQ_s_b4wa_m, pars = c("b_Intercept[1]","b_Intercept[2]","b_Intercept[3]","b_Intercept[4]","b_Intercept[5]","b_Intercept[6]", "b_MLQ_s_b4wa_typeMLQ_b_s_score", "sd_ID__Intercept", "sd_MLQ_QN__Intercept" )) + theme_classic()



## hypothesis testing  b2wa
hypothesis(MLQ_s_b4wa_m, "MLQ_s_b4wa_typeMLQ_b_s_score > 0")
plot(hypothesis(MLQ_s_b4wa_m, "MLQ_s_b4wa_typeMLQ_b_s_score < 0"))

conditional_effects(MLQ_s_b4wa_m, categorical = TRUE)
```


## Pb2wa Confounds
MLQ first dimension presence, before vs 2 weeks after possible confounds: mental health, other psychedelic expriences, placebo, psychedelic naive
```{r}
########################################### null model ##############################################
MLQ_2wa_null_f <- bf (MLQ_2wa_p_score ~ 1 +  MLQ_b_p_score + (1 | ID) + (1 | MLQ_QN))


get_prior(MLQ_2wa_null_f, MLQ, family = cumulative())


MLQ_2wa_null_prior <- c(
  prior(student_t(3, 0, 10), class = Intercept),
  prior(normal(0, .5), class = b, coef = "MLQ_b_p_score"),
  prior(normal(0, .5),   class = sd)
)

MLQ_2wa_null_mp <- brm(
  formula = MLQ_2wa_null_f,
  data = MLQ,
  family = cumulative("probit"),
  prior = MLQ_2wa_null_prior,
  sample_prior = "only",
  chains = 3,
  cores = 3,
  control = list(max_treedepth = 10, adapt_delta = 0.80))

# prior check 
summary(MLQ_2wa_null_mp)
pp_check(MLQ_2wa_null_mp, type = "bars", nsamples = 100)
  
## posterior model b2wa
MLQ_2wa_null_m<- brm(
  formula = MLQ_2wa_null_f,
  data = MLQ,
  family = cumulative("probit"),
  prior = MLQ_2wa_null_prior,
  sample_prior = T,
  chains = 3,
  cores = 3,
  iter = 2000,
  inits = 0,
  control = list(max_treedepth = 15, adapt_delta = 0.95),
  file = "model_files/MLQ_2wa_null_ranIn")

## pp checks b2wa
pp_check(MLQ_2wa_null_m, type = "bars", nsamples = 100)

summary(MLQ_2wa_null_m)

plot(MLQ_2wa_null_m)

## chain check b2wa
mcmc_trace(MLQ_2wa_null_m, pars = "b_MLQ_b_p_score") + theme_classic()

mcmc_rank_overlay(MLQ_2wa_null_m, pars = "b_MLQ_b_p_score") + theme_classic()


## hypothesis testing  b2wa
hypothesis(MLQ_p_b2wa_m2, "MLQ_b_p_score > 0")
plot(hypothesis(MLQ_p_b2wa_m2, "MLQ_b_p_score > 0"))

########################### Other Psychedelic experience ##############################################

# formula
MLQ_2wa_oPE_f <- bf (MLQ_2wa_p_score ~ 1 +  MLQ_b_p_score + Other_PE_2wa +(1|ID) + (1|MLQ_QN))


get_prior(MLQ_2wa_oPE_f, MLQ, family = cumulative())


MLQ_2wa_oPE_prior <- c(
  prior(student_t(3, 0, 10), class = Intercept),
  prior(normal(0, 1), class = b, coef = "MLQ_b_p_score"),
  prior(normal(0, 1), class = b, coef = "Other_PE_2waYes"),
  prior(normal(0, .5),   class = sd)
)

MLQ_2wa_oPE_mp <- brm(
  formula = MLQ_2wa_oPE_f,
  data = MLQ,
  family = cumulative("probit"),
  prior = MLQ_2wa_oPE_prior,
  sample_prior = "only",
  chains = 3,
  cores = 3,
  control = list(max_treedepth = 10, adapt_delta = 0.80))

# prior check 
summary(MLQ_2wa_oPE_mp)
pp_check(MLQ_2wa_oPE_mp, type = "bars", nsamples = 100)
  
## posterior model b2wa
MLQ_2wa_oPE_m<- brm(
  formula = MLQ_2wa_oPE_f,
  data = MLQ,
  family = cumulative("probit"),
  prior = MLQ_2wa_oPE_prior,
  sample_prior = T,
  chains = 3,
  cores = 3,
  iter = 2000,
  inits = 0,
  control = list(max_treedepth = 15, adapt_delta = 0.95),
  file = "model_files/MLQ_2wa_oPE")

## pp checks b2wa
pp_check(MLQ_2wa_oPE_m, type = "bars", nsamples = 100)

summary(MLQ_2wa_oPE_m)

plot(MLQ_2wa_oPE_m)

## chain check b2wa
mcmc_trace(MLQ_2wa_oPE_m, pars = c("b_MLQ_b_p_score", "b_Other_PE_2waYes" )) + theme_classic()

mcmc_rank_overlay(MLQ_2wa_oPE_m, pars = c("b_MLQ_b_p_score", "b_Other_PE_2waYes" )) + theme_classic()


## hypothesis testing  b2wa
hypothesis(MLQ_2wa_oPE_m, "Other_PE_2waYes < 0")
plot(hypothesis(MLQ_2wa_oPE_m, "Other_PE_2waYes < 0"))

###################################### Placebo effect #################################################

# formula
MLQ_2wa_placebo_f <- bf (MLQ_2wa_p_score ~ 1 +  MLQ_b_p_score +  Confidence_in_long_lasting_effect_PE + (1|ID) + (1|MLQ_QN))


get_prior(MLQ_2wa_placebo_f, MLQ, family = cumulative())


MLQ_2wa_placebo_prior <- c(
  prior(student_t(3, 0, 10), class = Intercept),
  prior(normal(0, 1), class = b, coef = "MLQ_b_p_score"),
  prior(normal(0, 1), class = b, coef = "Confidence_in_long_lasting_effect_PE"),
  prior(normal(0, .5),   class = sd)
)

MLQ_2wa_placebo_mp <- brm(
  formula = MLQ_2wa_placebo_f,
  data = MLQ,
  family = cumulative("probit"),
  prior = MLQ_2wa_placebo_prior,
  sample_prior = "only",
  chains = 3,
  cores = 3,
  control = list(max_treedepth = 10, adapt_delta = 0.80))

# prior check 
summary(MLQ_2wa_placebo_mp)
pp_check(MLQ_2wa_placebo_mp, type = "bars", nsamples = 100)
  
## posterior model b2wa
MLQ_2wa_placebo_m<- brm(
  formula = MLQ_2wa_placebo_f,
  data = MLQ,
  family = cumulative("probit"),
  prior = MLQ_2wa_placebo_prior,
  sample_prior = T,
  chains = 3,
  cores = 3,
  iter = 2000,
  inits = 0,
  control = list(max_treedepth = 15, adapt_delta = 0.95),
  file = "model_files/MLQ_2wa_placebo")

## pp checks b2wa
pp_check(MLQ_2wa_placebo_m, type = "bars", nsamples = 100)

summary(MLQ_2wa_placebo_m)

plot(MLQ_2wa_placebo_m)

## chain check b2wa
mcmc_trace(MLQ_2wa_placebo_m, pars = c("b_MLQ_b_p_score", "b_Other_PE_2waYes", "b_Confidence_in_long_lasting_effect_PE")) + theme_classic()

mcmc_rank_overlay(MLQ_2wa_placebo_m, pars = c("b_MLQ_b_p_score", "b_Other_PE_2waYes", "b_Confidence_in_long_lasting_effect_PE")) + theme_classic()


## hypothesis testing  b2wa
hypothesis(MLQ_2wa_placebo_m, "Confidence_in_long_lasting_effect_PE > 0")
plot(hypothesis(MLQ_2wa_placebo_m, "Confidence_in_long_lasting_effect_PE > 0"))

hypothesis(MLQ_2wa_placebo_m, "Other_PE_2waYes < 0")

###################################### Mental health #################################################

# formula
MLQ_2wa_ment_heal_f <- bf (MLQ_2wa_p_score ~ 1 +  MLQ_b_p_score + Other_PE_2wa + Confidence_in_long_lasting_effect_PE + Mental_health +(1|ID) + (1|MLQ_QN))


get_prior(MLQ_2wa_ment_heal_f, MLQ, family = cumulative())


MLQ_2wa_ment_heal_prior <- c(
  prior(student_t(3, 0, 10), class = Intercept),
  prior(normal(0, 1), class = b, coef = "MLQ_b_p_score"),
  prior(normal(0, 1), class = b, coef = "Other_PE_2waYes"),
  prior(normal(0, 1), class = b, coef = "Confidence_in_long_lasting_effect_PE"),
  prior(normal(0, 1), class = b, coef = "Mental_healthHealthy"),
  prior(normal(0, .5),   class = sd)
)

MLQ_2wa_ment_heal_mp <- brm(
  formula = MLQ_2wa_ment_heal_f,
  data = MLQ,
  family = cumulative("probit"),
  prior = MLQ_2wa_ment_heal_prior,
  sample_prior = "only",
  chains = 3,
  cores = 3,
  control = list(max_treedepth = 10, adapt_delta = 0.80))

# prior check 
summary(MLQ_2wa_ment_heal_mp)
pp_check(MLQ_2wa_ment_heal_mp, type = "bars", nsamples = 100)
  
## posterior model 
MLQ_2wa_ment_heal_m<- brm(
  formula = MLQ_2wa_ment_heal_f,
  data = MLQ,
  family = cumulative("probit"),
  prior = MLQ_2wa_ment_heal_prior,
  sample_prior = T,
  chains = 3,
  cores = 3,
  iter = 2000,
  inits = 0,
  control = list(max_treedepth = 15, adapt_delta = 0.95),
  file = "model_files/MLQ_2wa_mental_health")

## pp checks b2wa
pp_check(MLQ_2wa_ment_heal_m, type = "bars", nsamples = 100)

summary(MLQ_2wa_ment_heal_m)

plot(MLQ_2wa_ment_heal_m)

## chain check b2wa
mcmc_trace(MLQ_2wa_ment_heal_m, pars = c("b_MLQ_b_p_score", "b_Other_PE_2waYes", "b_Confidence_in_long_lasting_effect_PE", "b_Mental_healthHealthy")) + theme_classic()

mcmc_rank_overlay(MLQ_2wa_ment_heal_m, pars = c("b_MLQ_b_p_score", "b_Other_PE_2waYes", "b_Confidence_in_long_lasting_effect_PE", "b_Mental_healthHealthy")) + theme_classic()


## hypothesis testing  b2wa
hypothesis(MLQ_2wa_ment_heal_m, "Mental_healthHealthy > 0")
plot(hypothesis(MLQ_2wa_ment_heal_m, "Mental_healthHealthy > 0"))

hypothesis(MLQ_2wa_ment_heal_m, "Confidence_in_long_lasting_effect_PE > 0")
hypothesis(MLQ_2wa_ment_heal_m, "Other_PE_2waYes < 0")

###################################### Psychedelic naive ###############################################

# formula
MLQ_2wa_psych_naive_f <- bf (MLQ_2wa_p_score ~ 1 +  MLQ_b_p_score + Other_PE_2wa + Confidence_in_long_lasting_effect_PE + Mental_health + Psychedelic_naive + (1|ID) + (1|MLQ_QN))


get_prior(MLQ_2wa_psych_naive_f, MLQ, family = cumulative())


MLQ_2wa_psych_naive_prior <- c(
  prior(student_t(3, 0, 10), class = Intercept),
  prior(normal(0, 1), class = b, coef = "MLQ_b_p_score"),
  prior(normal(0, 1), class = b, coef = "Other_PE_2waYes"),
  prior(normal(0, 1), class = b, coef = "Confidence_in_long_lasting_effect_PE"),
  prior(normal(0, 1), class = b, coef = "Mental_healthHealthy"),
  prior(normal(0, 1), class = b, coef = "Psychedelic_naiveYes"),
  prior(normal(0, .5),   class = sd)
)

MLQ_2wa_psych_naive_mp <- brm(
  formula = MLQ_2wa_psych_naive_f,
  data = MLQ,
  family = cumulative("probit"),
  prior = MLQ_2wa_psych_naive_prior,
  sample_prior = "only",
  chains = 3,
  cores = 3,
  control = list(max_treedepth = 10, adapt_delta = 0.80))

# prior check 
summary(MLQ_2wa_psych_naive_mp)
pp_check(MLQ_2wa_psych_naive_mp, type = "bars", nsamples = 100)
  
## posterior model 
MLQ_2wa_psych_naive_m<- brm(
  formula = MLQ_2wa_psych_naive_f,
  data = MLQ,
  family = cumulative("probit"),
  prior = MLQ_2wa_psych_naive_prior,
  sample_prior = T,
  chains = 3,
  cores = 3,
  iter = 2000,
  inits = 0,
  control = list(max_treedepth = 15, adapt_delta = 0.95),
  file = "model_files/MLQ_2wa_psych_naive")

## pp checks b2wa
pp_check(MLQ_2wa_psych_naive_m, type = "bars", nsamples = 100)

summary(MLQ_2wa_psych_naive_m)

plot(MLQ_2wa_psych_naive_m)

## chain check b2wa
mcmc_trace(MLQ_2wa_psych_naive_m, pars = c("b_MLQ_b_p_score", "b_Other_PE_2waYes", "b_Confidence_in_long_lasting_effect_PE", "b_Mental_healthHealthy", "b_Psychedelic_naiveYes")) + theme_classic()

mcmc_rank_overlay(MLQ_2wa_psych_naive_m, pars = c("b_MLQ_b_p_score", "b_Other_PE_2waYes", "b_Confidence_in_long_lasting_effect_PE", "b_Mental_healthHealthy", "b_Psychedelic_naiveYes")) + theme_classic()


## hypothesis testing  b2wa
hypothesis(MLQ_2wa_psych_naive_m, "Psychedelic_naiveYes > 0")
plot(hypothesis(MLQ_2wa_psych_naive_m, "Psychedelic_naiveYes > 0"))
 
###  other variables
hypothesis(MLQ_2wa_psych_naive_m, "Mental_healthHealthy > 0")
hypothesis(MLQ_2wa_psych_naive_m, "Confidence_in_long_lasting_effect_PE > 0")
hypothesis(MLQ_2wa_psych_naive_m, "Other_PE_2waYes < 0")

######################################### comparing models #############################################

## adding criterions
MLQ_2wa_null_m <- add_criterion(MLQ_2wa_null_m, criterion = "loo")

MLQ_2wa_oPE_m <- add_criterion(MLQ_2wa_oPE_m, criterion = "loo")

MLQ_2wa_placebo_m <- add_criterion(MLQ_2wa_placebo_m, criterion = "loo")

MLQ_2wa_ment_heal_m <- add_criterion(MLQ_2wa_ment_heal_m, criterion = "loo")

MLQ_2wa_psych_naive_m <- add_criterion(MLQ_2wa_psych_naive_m, criterion = "loo")


## comparison
MLQ_2wa_loo <- loo_compare(MLQ_2wa_null_m, MLQ_2wa_oPE_m, MLQ_2wa_placebo_m, MLQ_2wa_ment_heal_m, MLQ_2wa_psych_naive_m)
MLQ_2wa_loo

MLQ_2wa_loo_weights <- loo_model_weights(MLQ_2wa_null_m, MLQ_2wa_oPE_m, MLQ_2wa_placebo_m, MLQ_2wa_ment_heal_m, MLQ_2wa_psych_naive_m)
MLQ_2wa_loo_weights

loo_model_weights(MLQ_2wa_null_m, MLQ_2wa_psych_naive_m)

```


## Pb2wa predicting
MLQ presence, before vs 2 weeks after, predicting from 5 questionnaires + confounds
```{r}
MLQ_2wa_pred_f <- 
  bf (MLQ_2wa_p_score ~ 1 +  MLQ_b_p_score + Confidence_in_long_lasting_effect_PE + Mental_health + MEQ_scale + EDI_scale + EBI_scale + ASC_scale + CEQ_scale + (1|ID) + (1|MLQ_QN))


get_prior(MLQ_2wa_pred_f, MLQ, family = cumulative())


MLQ_2wa_pred_prior <- c(
  prior(student_t(3, 0, 10), class = Intercept),
  prior(normal(0, 1), class = b, coef = "MLQ_b_p_score"),
  prior(normal(0, 1), class = b, coef = "Confidence_in_long_lasting_effect_PE"),
  prior(normal(0, 1), class = b, coef = "Mental_healthHealthy"),
  prior(normal(0, .5),   class = sd),
  prior(normal(0, 1), class = b, coef = "MEQ_scale"),
  prior(normal(0, 1), class = b, coef = "EDI_scale"),
  prior(normal(0, 1), class = b, coef = "EBI_scale"),
  prior(normal(0, 1), class = b, coef = "ASC_scale"),
  prior(normal(0, 1), class = b, coef = "CEQ_scale")
)

MLQ_2wa_pred_mp <- brm(
  formula = MLQ_2wa_pred_f,
  data = MLQ,
  family = cumulative("probit"),
  prior = MLQ_2wa_pred_prior,
  sample_prior = "only",
  chains = 3,
  cores = 3,
  control = list(max_treedepth = 10, adapt_delta = 0.80))

# prior check 
summary(MLQ_2wa_pred_mp)
pp_check(MLQ_2wa_pred_mp, type = "bars", nsamples = 100)
  
## posterior model 
MLQ_2wa_pred_m<- brm(
  formula = MLQ_2wa_pred_f,
  data = MLQ,
  family = cumulative("probit"),
  prior = MLQ_2wa_pred_prior,
  sample_prior = T,
  chains = 3,
  cores = 3,
  iter = 2000,
  inits = 0,
  control = list(max_treedepth = 15, adapt_delta = 0.95),
  file = "model_files/MLQ_2wa_pred1")

## pp checks b2wa
pp_check(MLQ_2wa_pred_m, type = "bars", nsamples = 100)

summary(MLQ_2wa_pred_m)

plot(MLQ_2wa_pred_m)

## chain check b2wa
mcmc_trace(MLQ_2wa_pred_m, pars = c("b_MLQ_b_p_score", "b_Other_PE_2waYes", "b_Confidence_in_long_lasting_effect_PE", "b_Mental_healthHealthy", "b_Psychedelic_naiveYes")) + theme_classic()

mcmc_rank_overlay(MLQ_2wa_pred_m, pars = c("b_MLQ_b_p_score", "b_Other_PE_2waYes", "b_Confidence_in_long_lasting_effect_PE", "b_Mental_healthHealthy", "b_Psychedelic_naiveYes")) + theme_classic()


## hypothesis testing  b2wa
hypothesis(MLQ_2wa_pred_m, "MEQ_scale > 0")
plot(hypothesis(MLQ_2wa_pred_m, "MEQ_scale > 0"))
 
hypothesis(MLQ_2wa_pred_m, "EDI_scale > 0")
plot(hypothesis(MLQ_2wa_pred_m, "EDI_scale > 0"))

hypothesis(MLQ_2wa_pred_m, "EBI_scale > 0")
plot(hypothesis(MLQ_2wa_pred_m, "EBI_scale > 0"))

hypothesis(MLQ_2wa_pred_m, "ASC_scale < 0")
plot(hypothesis(MLQ_2wa_pred_m, "ASC_scale < 0"))

hypothesis(MLQ_2wa_pred_m, "CEQ_scale < 0")
plot(hypothesis(MLQ_2wa_pred_m, "CEQ_scale < 0"))


conditional_effects()
################# Pb2wa predicting interaction #################

MLQ_2wa_pred_Inter_f <- 
  bf (MLQ_b_p_score ~ 1 +  Other_PE_2wa + Confidence_in_long_lasting_effect_PE + Mental_health + Psychedelic_naive + MLQ_b_p_score:MEQ_scale + MLQ_b_p_score:EDI_scale + MLQ_b_p_score:EBI_scale + MLQ_b_p_score:ASC_scale + MLQ_b_p_score:CEQ_scale + (1|ID) + (1|MLQ_QN))


get_prior(MLQ_2wa_pred_Inter_f, MLQ, family = cumulative())


MLQ_2wa_pred_Inter_prior <- c(
  prior(student_t(3, 0, 10), class = Intercept),
  #prior(normal(0, 1), class = b, coef = "MLQ_b_p_score"),
  prior(normal(0, 1), class = b, coef = "Other_PE_2waYes"),
  prior(normal(0, 1), class = b, coef = "Confidence_in_long_lasting_effect_PE"),
  prior(normal(0, 1), class = b, coef = "Mental_healthHealthy"),
  prior(normal(0, 1), class = b, coef = "Psychedelic_naiveYes"),
  prior(normal(0, .5),   class = sd),
  prior(normal(0, 1), class = b, coef = "MLQ_b_p_score:MEQ_scale"),
  prior(normal(0, 1), class = b, coef = "MLQ_b_p_score:EDI_scale"),
  prior(normal(0, 1), class = b, coef = "MLQ_b_p_score:EBI_scale"),
  prior(normal(0, 1), class = b, coef = "MLQ_b_p_score:ASC_scale"),
  prior(normal(0, 1), class = b, coef = "MLQ_b_p_score:CEQ_scale")
)

MLQ_2wa_pred_Inter_mp <- brm(
  formula = MLQ_2wa_pred_Inter_f,
  data = MLQ,
  family = cumulative("probit"),
  prior = MLQ_2wa_pred_Inter_prior,
  sample_prior = "only",
  chains = 3,
  cores = 3,
  control = list(max_treedepth = 10, adapt_delta = 0.80))

# prior check 
summary(MLQ_2wa_pred_Inter_mp)
pp_check(MLQ_2wa_pred_Inter_mp, type = "bars", nsamples = 100)
  
## posterior model 
MLQ_2wa_pred_Inter_m<- brm(
  formula = MLQ_2wa_pred_Inter_f,
  data = MLQ,
  family = cumulative("probit"),
  prior = MLQ_2wa_pred_Inter_prior,
  sample_prior = T,
  chains = 3,
  cores = 3,
  iter = 2000,
  inits = 0,
  control = list(max_treedepth = 15, adapt_delta = 0.95),
  file = "model_files/MLQ_2wa_pred_Inter_ques3Absurd")

## pp checks b2wa
pp_check(MLQ_2wa_pred_Inter_m, type = "bars", nsamples = 100)

summary(MLQ_2wa_pred_Inter_m)

plot(MLQ_2wa_pred_Inter_m)

## chain check b2wa
mcmc_trace(MLQ_2wa_pred_Inter_m, pars = c("b_MLQ_b_p_score", "b_Other_PE_2waYes", "b_Confidence_in_long_lasting_effect_PE", "b_Mental_healthHealthy", "b_Psychedelic_naiveYes")) + theme_classic()

mcmc_rank_overlay(MLQ_2wa_pred_Inter_m, pars = c("b_MLQ_b_p_score", "b_Other_PE_2waYes", "b_Confidence_in_long_lasting_effect_PE", "b_Mental_healthHealthy", "b_Psychedelic_naiveYes")) + theme_classic()


## hypothesis testing  b2wa
hypothesis(MLQ_2wa_pred_Inter_m, "MLQ_b_p_score:MEQ_scale > 0")
plot(hypothesis(MLQ_2wa_pred_Inter_m, "MLQ_b_p_score:MEQ_scale > 0"))
 
hypothesis(MLQ_2wa_pred_Inter_m, "MLQ_b_p_score:EDI_scale > 0")
plot(hypothesis(MLQ_2wa_pred_Inter_m, "MLQ_b_p_score:EDI_scale > 0"))

hypothesis(MLQ_2wa_pred_Inter_m, "MLQ_b_p_score:EBI_scale > 0")
plot(hypothesis(MLQ_2wa_pred_Inter_m, "MLQ_b_p_score:EBI_scale > 0"))

hypothesis(MLQ_2wa_pred_Inter_m, "MLQ_b_p_score:ASC_scale < 0")
plot(hypothesis(MLQ_2wa_pred_Inter_m, "MLQ_b_p_score:ASC_scale < 0"))

hypothesis(MLQ_2wa_pred_Inter_m, "MLQ_b_p_score:CEQ_scale < 0")
plot(hypothesis(MLQ_2wa_pred_Inter_m, "MLQ_b_p_score:CEQ_scale < 0"))

conditional_effects(MLQ_2wa_pred_Inter_m, categorical = TRUE, conditions = MLQ$ASC_scale)



```




##Pb4wa confounds
MLQ first dimension presence, before vs 4 weeks after possible confounds: mental health, other psychedelic expriences, placebo, psychedelic naive
```{r}
# formula
MLQ_4wa_confound_f <- bf (MLQ_2wa_p_score ~ 1 +  MLQ_b_p_score + Other_PE_4wa+  Confidence_in_long_lasting_effect_PE + Mental_health + Psychedelic_naive +  (1|ID) + (1| MLQ_QN))


get_prior(MLQ_4wa_confound, MLQ, family = cumulative())


MLQ_4wa_confound_prior <- c(
  prior(student_t(3, 0, 10), class = Intercept),
  prior(normal(0, 1), class = b, coef = "MLQ_b_p_score"),
  prior(normal(0, 1), class = b, coef = "Other_PE_4waYes"),
  prior(normal(0, 1), class = b, coef = "Confidence_in_long_lasting_effect_PE"),
  prior(normal(0, 1), class = b, coef = "Mental_healthHealthy"),
  prior(normal(0, 0.5), class = b, coef = "Psychedelic_naiveYes"),
  prior(normal(0, .5),   class = sd)
)

MLQ_4wa_confound_mp <- brm(
  formula = MLQ_4wa_confound_f,
  data = MLQ,
  family = cumulative("probit"),
  prior = MLQ_4wa_confound_prior,
  sample_prior = "only",
  chains = 3,
  cores = 3,
  control = list(max_treedepth = 10, adapt_delta = 0.80))

# prior check 
summary(MLQ_4wa_confound_mp)
pp_check(MLQ_4wa_confound_mp, type = "bars", nsamples = 100)
  
## posterior model 
MLQ_4wa_confound_m<- brm(
  formula = MLQ_4wa_confound_f,
  data = MLQ,
  family = cumulative("probit"),
  prior = MLQ_4wa_confound_prior,
  sample_prior = T,
  chains = 3,
  cores = 3,
  iter = 2000,
  inits = 0,
  control = list(max_treedepth = 15, adapt_delta = 0.95),
  file = "model_files/MLQ_4wa_confound5")

## pp checks b2wa
pp_check(MLQ_4wa_confound_m, type = "bars", nsamples = 100)

summary(MLQ_4wa_confound_m)

plot(MLQ_4wa_confound_m)

## chain check b2wa
mcmc_trace(MLQ_4wa_confound_mp, pars = c("b_MLQ_b_p_score", "b_Other_PE_2waYes", "b_Confidence_in_long_lasting_effect_PE", "b_Mental_healthHealthy", "b_Psychedelic_naiveYes")) + theme_classic()

mcmc_rank_overlay(MLQ_4wa_confound_mp, pars = c("b_MLQ_b_p_score", "b_Other_PE_2waYes", "b_Confidence_in_long_lasting_effect_PE", "b_Mental_healthHealthy", "b_Psychedelic_naiveYes")) + theme_classic()


## hypothesis testing  b2wa
hypothesis(MLQ_4wa_confound_mp, "Psychedelic_naiveYes > 0")
plot(hypothesis(MLQ_4wa_confound_mp, "Psychedelic_naiveYes > 0"))
 
###  other variables
hypothesis(MLQ_4wa_confound_mp, "Mental_healthHealthy > 0")
hypothesis(MLQ_4wa_confound_mp, "Confidence_in_long_lasting_effect_PE > 0")
hypothesis(MLQ_4wa_confound_mp, "Other_PE_2waYes < 0")




```

## Pb4wa predicting
MLQ presence, before vs 2 weeks after, predicting from 5 questionnaires + confounds
```{r}
MLQ_4wa_pred_f <- 
  bf (MLQ_4wa_p_score ~ 1 +  MLQ_b_p_score + Other_PE_4wa + Confidence_in_long_lasting_effect_PE + Mental_health + Psychedelic_naive + MEQ_scale + EDI_scale + EBI_scale + ASC_scale + CEQ_scale + (1|ID) + (1|MLQ_QN))


get_prior(MLQ_4wa_pred_f, MLQ, family = cumulative())


MLQ_4wa_pred_prior <- c(
  prior(student_t(3, 0, 10), class = Intercept),
  prior(normal(0, 1), class = b, coef = "MLQ_b_p_score"),
  prior(normal(0, 1), class = b, coef = "Mental_healthHealthy"),
  prior(normal(0, 1), class = b, coef = "Psychedelic_naiveYes"),
  prior(normal(0, 1), class = b, coef = "Confidence_in_long_lasting_effect_PE"),
  prior(normal(0, 1), class = b, coef = "Other_PE_4waYes"),
  prior(normal(0, .5),   class = sd),
  prior(normal(0, 1), class = b, coef = "MEQ_scale"),
  prior(normal(0, 1), class = b, coef = "EDI_scale"),
  prior(normal(0, 1), class = b, coef = "EBI_scale"),
  prior(normal(0, 1), class = b, coef = "ASC_scale"),
  prior(normal(0, 1), class = b, coef = "CEQ_scale")
)

MLQ_4wa_pred_mp <- brm(
  formula = MLQ_4wa_pred_f,
  data = MLQ,
  family = cumulative("probit"),
  prior = MLQ_4wa_pred_prior,
  sample_prior = "only",
  chains = 3,
  cores = 3,
  control = list(max_treedepth = 10, adapt_delta = 0.80))

# prior check 
summary(MLQ_4wa_pred_mp)
pp_check(MLQ_4wa_pred_mp, type = "bars", nsamples = 100)
  
## posterior model 
MLQ_4wa_pred_m<- brm(
  formula = MLQ_4wa_pred_f,
  data = MLQ,
  family = cumulative("probit"),
  prior = MLQ_4wa_pred_prior,
  sample_prior = T,
  chains = 3,
  cores = 3,
  iter = 2000,
  inits = 0,
  control = list(max_treedepth = 15, adapt_delta = 0.95),
  file = "model_files/MLQ_4wa_pred2")

## pp checks b2wa
pp_check(MLQ_4wa_pred_m, type = "bars", nsamples = 100)

summary(MLQ_4wa_pred_m)

plot(MLQ_4wa_pred_m)

## chain check b2wa
mcmc_trace(MLQ_4wa_pred_m, pars = c("b_MLQ_b_p_score", "b_Other_PE_2waYes", "b_Confidence_in_long_lasting_effect_PE", "b_Mental_healthHealthy", "b_Psychedelic_naiveYes")) + theme_classic()

mcmc_rank_overlay(MLQ_4wa_pred_m, pars = c("b_MLQ_b_p_score", "b_Other_PE_2waYes", "b_Confidence_in_long_lasting_effect_PE", "b_Mental_healthHealthy", "b_Psychedelic_naiveYes")) + theme_classic()


## hypothesis testing  b2wa
hypothesis(MLQ_4wa_pred_m, "MEQ_scale > 0")
plot(hypothesis(MLQ_4wa_pred_m, "MEQ_scale > 0"))
 
hypothesis(MLQ_4wa_pred_m, "EDI_scale > 0")
plot(hypothesis(MLQ_4wa_pred_m, "EDI_scale > 0"))

hypothesis(MLQ_4wa_pred_m, "EBI_scale > 0")
plot(hypothesis(MLQ_4wa_pred_m, "EBI_scale > 0"))

hypothesis(MLQ_4wa_pred_m, "ASC_scale < 0")
plot(hypothesis(MLQ_4wa_pred_m, "ASC_scale < 0"))

hypothesis(MLQ_4wa_pred_m, "CEQ_scale < 0")
plot(hypothesis(MLQ_4wa_pred_m, "CEQ_scale < 0"))

hypothesis(MLQ_4wa_pred_m, "Mental_healthHealthy > 0")
hypothesis(MLQ_4wa_pred_m, "Psychedelic_naiveYes > 0")
conditional_effects(MLQ_4wa_pred_m, categorical = TRUE)

```











